Comparing Generative Pre-trained Transformer Models to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-07-06 manuscript/manuscript.tex
Finish discussion

\subsubsection{Comparable to Physicians for Some Causes of Death}\label{discuss-adv-cod}

@@

\subsubsection{Verbal Autopsy Integration}\label{discuss-opp-vaint}

Physician assisted verbal autopsy coding.

>>>>

\subsubsection{Performant for Particular Causes of Death}\label{discuss-adv-cod}

@@

\subsubsection{Computer Assisted Verbal Autopsy}\label{discuss-opp-vaint}

Another research opportunity is in the integration of GPT, InterVA-5, and InSilicoVA models into VA systems to assist physicians in COD assignment. In dual-coded VA systems (described in Section \ref{methods-data}), two physicians are randomly assigned to each record and require second inspections of each other's assignment (reconciliation) and evaluation by a third more senior physician if their assignments do not agree. As mentioned in Section \ref{discuss-adv-efficient}, suggestion of alternative assignments from GPT and InSilicoVA models potentially reduces the disagreement between physicians, and ill-defined records, while allowing physicians to focus on more difficult records. Thus, model suggestions can be integrated into VA systems by presenting model suggestions to physicians after their initial COD assignment, which allows them to consider alternative assignments and possibly revise their assignments based on the suggestions (Figure \ref{fig-discuss-phyassist}). Our future work will assess the effects of these model suggestions on physician assignment outcomes (e.g. increase in agreed records, reduction of ill-defined deaths). In preparation, we have integrated GPT-4, InterVA-5, and InSilicoVA model suggestions into our HEAL-SL study for after survey round 2 \cite{njalauniversityHealthySierraLeone2023}.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.98\textwidth]{fig-discuss-phyassist.pdf}
    \caption{Addition of model suggestions into physician assignment process. GPT, InterVA-5, and InSilicoVA models can suggest COD assignments to consider, providing the option to revise or proceed with their initial assignment. The additional consideration potentially reduces disagreement between physicians and ill-defined deaths.}\label{fig-discuss-phyassist}
\end{figure}
